---
title: "Test"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

```{r eval = FALSE}
## packages you might need
install.packages("devtools")
library(devtools)
install.packages("RCurl")
devtools:::install_github("omegahat/RCurl")  # other option
install.packages("XML")
devtools:::install_github("ajabadi/XMLRPC", ref = "patch-2") ## informative error when 'Problems' occurs
devtools:::install_github("duncantl/RWordPress")
```

```{r}
library(RWordPress)
library(XML)
library(RCurl)
library(knitr)
## functon to upload images
opts_knit$set(upload.fun = imgur_upload, base.url = NULL) 
```


# Credentials

Save your credentials as indicated below in `__wp_credentials.R`. It is ignored in .gitignore. Run it before proceeding.

```{r}
# Set your WP username, password, and your site URL
 options(WordpressLogin = c(maxbladen = ''), #update these
         WordpressURL = 'http://mixomics.org/xmlrpc.php')
# note: you may have to play around with the following options 'http://mixomics.org/xmlrpc.php' (http, not https)
```

```{r}
## instead 
source("../__wp_credentials.R")
```

# Rmd files

**Find the 'title's from src/Submit_Rmd_to_mixOmics.org.R**

## Test

Make sure this test works (successfully knits, return a number and shows up in drafts) and `Trash` it from `Pages > Drafts`:

```{r}
knit2wp(input = '__Test.Rmd', title = 'this is a test',  shortcode = FALSE, publish = FALSE, 
        action = c("newPage"))
```


```{r}
# more advanced test
knit2wp(input = '__Test2.Rmd', title = 'this is a test2',  shortcode = FALSE, publish = FALSE, 
        action = c("newPage"))
```

```{r}
# current test
knit2wp(input = 'Test3.Rmd', title = 'Test3',  shortcode = FALSE, publish = FALSE, 
        action = c("newPage"))
```
**Now, move on to src/Submit_Rmd_to_mixOmics.org.R to update each page (not in bulk!)**

GUIDELINES: the new files will be sent to drafts on wordpress

1 - go to the updated page in Pages/drafts, preview, then 'quick edit' then 'publish'

2 - trash the existing file in Pages/Published

3 - in Pages/published, then 'quick edit' then choose parent page (probably not super useful) 

4 - Go to Appearance/Menu, add the nuw page to menu (will be append at the bottom) then reorganise the tab then 'save menu'

5 - check on website


**List of potential errors / things to check:**

- if SSL error, check the credentials, as it could be WordpressURL = 'http://mixomics.org/xmlrpc.php OR 'http://mixomics.org/xmlrpc.php' (http, not https) (for example Al is https, and KA is http)

- if Bad Request (HTTP 400) or time out, keep trying. The server is just not responding

- text in comment in the Rmd text (it is ok in the code)

- Headings very similar to the title. Remove any first heading in the document

- check references weblinks: maybe too long

- for CIM / networks, put out.width='30%' in the chunk



<!-- Could read this further for bugs (scroll end of page): http://tobiasdienlin.com/2019/03/08/how-to-publish-a-blog-post-on-wordpress-using-rmarkdown/ -->

